### 2018-02-08 plos-latex-template/manuscript.Rnw
include results in manuscript and sort things around a bit

\section*{Results}
We present an small example examining the circadian behaviour of 128 fruit flies in recorded in a DAM2 -- a paradigm very widely adopted. 
A less formal description of this case and others are explained at \href{https://rethomics.github.io/}{https://rethomics.github.io/}.
In order to prodive a more comprehensive and didactic example, data was altered and simplified.	
Fig~\ref{fig:experiment} describes our case experiment (A) and the corresponding metadata (B).
Briefly, three monitors were used each containing 16 males and 16 females of a different genotype (A, B and C).
Two replicates were performed at different times.
raw data and metadata files are publicly available TODO cite zenodo

\subsection*{Data loading}

\subsection*{Quality control}

\subsection*{Actograms}

\subsection*{Spectogram}

>>>>

<<'child-results.Rnw', child='results.Rnw'>>=
@

% We present an small example examining the circadian behaviour of 128 fruit flies in recorded in a DAM2 -- a paradigm very widely adopted. 
% A less formal description of this case and others are explained at \href{https://rethomics.github.io/}{https://rethomics.github.io/}.
% In order to prodive a more comprehensive and didactic example, data was altered and simplified.	
% Fig~\ref{fig:experiment} describes our case experiment (A) and the corresponding metadata (B).
% Briefly, three monitors were used each containing 16 males and 16 females of a different genotype (A, B and C).
% Two replicates were performed at different times.
% raw data and metadata files are publicly available TODO cite zenodo
%
